---
title: "joinEasy"
output: html_document
---


```{r message=F}
library(joinEasy)
left <- data.frame(id = 100:106, letter = c('a', 'b', 'c', 'd', 'e', 'f', 'g'))
random_i <- sample(seq_len(nrow(left)))
cutpoint <- round(nrow(left) / 2)
right <- left[random_i[seq_len(cutpoint)],]
```


### anti_join
#### Returns the set of all tuples that are in neither the intersection of the two dataframes, nor in the right dataframe.
```{r}
anti_join(left, right, 'id')
# right for comparison:
right
```

### inner_join
#### Returns only those rows which are common to both dataframes.
```{r}
inner_join(left, right, 'id')
```

### left_outer_join
#### Returns only those rows which are either common to both dataframes or present only in the left dataframe.
```{r}
left_outer_join(left, right, 'id')
```

### semi_join
#### Returns a similar result to that of the inner_join, except that this one never duplicates rows.
```{r}
semi_join(left, right, 'id')
```

### cross_join
#### Returns the cartesian product of the two dataframes. This is the only exported function that cannot accept a primary key value.
```{r}
cross_join(left, right)
```
